---
title: "Bayesian Reliability Analysis"
runtime: shiny
output:
  html_document:
    toc: true
    toc_depth: 3
    css: custom.css
---

# Overview of Bayesian Reliability Analysis

Bayesian statistical methods 
flow chart picture

# Types of Analysis

Understanding the question of interest and organizing all relevant information is the key first step in any Bayesian statistical anyalysis.  

Reliability problems have a few common forms.

<div data-role="collapsible" data-collapsible = "true">
## Pass/Fail

data with binary outcomes = binomial likelihood
</div>
## Time to Failure

data that can take positive real number outcomes = exponential likelihood

# Building Prior

## Uninformative

## Informative

## Distributions

### Beta


$$ f(x|\alpha, \beta) \propto x^{\alpha - 1} (1-x)^{\beta -1} $$ 
```{r, echo = FALSE}
library(shiny)
library(ggplot2)
shinyApp(
  
  ui = shinyUI(fluidPage(
  
  column(12,
         ""),
  
  sidebarLayout(
    sidebarPanel(
    
      sliderInput("a", 
                  "Alpha:", 
                  value = 1,
                  min = .01, 
                  max = 10),
      sliderInput("b", 
                  "Beta:", 
                  value = 1,
                  min = 0.01, 
                  max = 10)
    ),
    mainPanel(
        plotOutput('plot1'),
        textOutput("summary")
    )
  )
)),
  
  server = function(input, output) {
  
  data1 <- reactiveValues()
  
  plot <- function(a,b){
    x <- seq(0.01,0.99,0.01)
    betaD <- dbeta(x,a,b)

    data1$beta <- data.frame(cbind(x, betaD))
    
    ggplot(data1$beta, aes(x=x, y=betaD)) + geom_line(colour="#CC0000") + ylab("Density")
    
  }  
  
  output$plot1 <- renderPlot({
    plot(input$a,input$b)
  })
  
  output$summary <- renderPrint({
    m <- input$a / (input$a + input$b)
    paste("Mean:", m)

  })

},
     options = list(height = 600)
)
```


### Gamma


$$ f(x|\alpha, \beta) \propto x^{\alpha - 1} e^{-\beta x} $$ 

```{r, echo = FALSE}
library(shiny)
library(ggplot2)
shinyApp(
  
  ui = shinyUI(fluidPage(
  
  column(12,
         ""),
  
  sidebarLayout(
    sidebarPanel(
    
      sliderInput("a", 
                  "Alpha:", 
                  value = 5,
                  min = .01, 
                  max = 10),
      sliderInput("b", 
                  "Beta:", 
                  value = 5,
                  min = 0.01, 
                  max = 10)
    ),
    mainPanel(
        plotOutput('plot1'),
        textOutput("summary")
    )
  )
)),
  
  server = function(input, output) {
  
  plot <- function(a,b){
    x <- seq(0, 10, 0.01)
    gammaD <- dgamma(x,a,b)

    d <- data.frame(cbind(x, gammaD))
    
    ggplot(d, aes(x=x, y=gammaD)) + geom_line(colour="#CC0000") + ylab("Density") +  coord_cartesian(xlim = c(0, 10)) + theme(axis.text.x = element_text(colour = "blue", size = 15, face = "italic"))
    
  }  
  
  output$plot1 <- renderPlot({
    plot(input$a,input$b)
  })
  
  output$summary <- renderPrint({
    m <- input$a / input$b
    paste("Mean:", m)

  })
},
  
  options = list(height = 600)
)
```


# Likelihood/Data

# Posterior/Results

# Examples
